---
title: "Leslie matrix example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

A population of fish we're interested in has four life stages: eggs (E), fry (F), juvenile (J), breeding adult (A). You are given the following:

- Each breeding adult will produce, on average, 600 eggs
- 25% of eggs will survive to become fry
- 10% of fry will survive to become juveniles
- 40% of juveniles will survive to become adults
- Adult survival rate year to year is 80%

### Create the matrix

```{r}
# Make the Leslie Matrix:
fish_leslie <- matrix(c(0, 0, 0, 600, 0.25, 0, 0, 0, 0, 0.10, 0, 0, 0, 0, 0.4, 0.8), nrow = 4, ncol = 4, byrow = TRUE)

# Check it out: 
fish_leslie
```

### Set the initial population structure

Initial population (Year 0): 0 eggs, 40,000 fry, 600 juveniles, and 450 adults.

```{r}
# Initial population structure (R, F, J, A): 
fish_year0 <- c(0, 40000, 600, 450)
```

### Project over several years 

```{r}
# Population structure in year 1:
fish_year1 <- fish_leslie %*% fish_year0
fish_year1

# Population structure in year 2: 
fish_year2 <- fish_leslie %*% fish_year1
fish_year2

# Population structure in year 3: 
fish_year3 <- fish_leslie %*% fish_year2
fish_year3

## ADD YOUR CODE TO PROJECT FOR YEARS 4, 5 & 6 HERE:
fish_year4 <- fish_leslie %*% fish_year3
fish_year4

fish_year5 <- fish_leslie %*% fish_year4
fish_year5

fish_year6 <- fish_leslie %*% fish_year5
fish_year6

```

